More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-08 2016-Weak-FH-Bisim/WeakBisim.tex
WEAK: removed a TODO and added a TODO section at the begining

\TODO{state clearly that the next two definitions are mutually dependent}

@@

The preceding definition relies on the auxiliary functions below:

\begin{definition}[Sorts, Holes, Leaves of pNets]
  \begin{itemize}
  \item The sort of a pNet is its signature, i.e. the set of actions it can
perform. In the definition of sorts, we do not need to distinguish
input variables (that specify the dataflow within LTSs), so for
computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
operation.} to remove the
\emph{input marker} of variables. Formally:
\[
\begin{array}{l}
\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
    J}\rangle} s'\in \to \} \\
\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
\overline{\pNet}\!,
\overline{\symb{SV}}\myrangle)
=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
\to\alpha'\in\set{\symb{SV}}\}
\end{array}
\]

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | e_b
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
\end{array} \bigg)\]
\LUDO{Is and g sufficient? I would say yes}

>>>>

We now define the structure of pNets, the following definition relies on the definition 
of holes, leaves and sorts provided below in Definition~\ref{def-sortholeleave}.

@@

The preceding definition relies on the auxiliary functions defined below:

\begin{definition}[Sorts, Holes, Leaves of pNets]\label{def-sortholeleave}
  \begin{itemize}
  \item The sort of a pNet is its signature, i.e. the set of actions it can
perform. In the definition of sorts, we do not need to distinguish
input variables (that specify the dataflow within LTSs), so for
computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
operation.} to remove the
\emph{input marker} of variables. Formally:
\[
\begin{array}{l}
\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
    J}\rangle} s'\in \to \} \\
\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
\overline{\pNet}\!,
\overline{\symb{SV}}\myrangle)
=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
\to\alpha'\in\set{\symb{SV}}\}
\end{array}
\]

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | e_b
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
\end{array} \bigg)\]
